### 2016-09-26 projects_that_depend_on_sympy.tex
Sage -> SageMath

\href{http://www.sagemath.org/}{\textbf{Sage}}~\cite{sagemath} &  & A CAS, visioned to be
  a viable free open source alternative to Magma, Maple, Mathematica and
  MATLAB\@. Sage includes many open source mathematical libraries, including
  SymPy. \\

>>>>

\href{http://www.sagemath.org/}{\textbf{SageMath}}~\cite{sagemath} &  & A CAS, visioned to be
  a viable free open source alternative to Magma, Maple, Mathematica and
  MATLAB\@. Sage includes many open source mathematical libraries, including
  SymPy. \\
